### 2021-12-06 doc/src/AdvPLIC.tex
Fix a couple of editing errors

PLICs that actually hardwire the IMSIC addresses internally
can implement these registers simply as read-only with values zero
and \z{0x80000000}.
Or, if the IMSIC addresses must be configured by software but
the formula is too complex for registers \z{mmsiaddrcfg} and
\z{mmsiaddrcfgh} to handle, again the registers can be implemented
simply as read-only with values zero and \z{8x00000000}, and a
separate, custom mechanism supplied for configuring the IMSIC
addresses.
\end{commentary}

>>>>

PLICs that actually hardwire the IMSIC addresses internally
can implement these registers simply as read-only with values zero
and \z{0x80000000}.
Or, if the IMSIC addresses must be configured by software but
the formula is too complex for registers \z{mmsiaddrcfg} and
\z{mmsiaddrcfgh} to handle, again the registers can be implemented
simply as read-only with values zero and \z{0x80000000}, and a
separate, custom mechanism supplied for configuring the IMSIC
addresses.
\end{commentary}

### 2021-12-06 doc/src/CSRs.tex
Add vstopei to CSR lists where forgotten
Fix a couple of editing errors

\begin{table*}[h!]
\begin{center}
\begin{tabular}{|l|l|l|l|}
\hline
Number & Privilege & Name        & Description \\
\hline
\hline
\multicolumn{4}{|c|}{%
  Virtual Interrupts and Interrupt Priorities for VS Level} \\
\hline
\z{0x608} & HRW & \z{hvien}      & Hypervisor virtual interrupt enables \\
\z{0x609} & HRW & \z{hvictl}     & Hypervisor virtual interrupt control \\
\z{0x646} & HRW & \z{hviprio1}   & Hypervisor VS-level interrupt priorities \\
\z{0x647} & HRW & \z{hviprio2}   & Hypervisor VS-level interrupt priorities \\
\hline
\multicolumn{4}{|c|}{VS-Level Window to Indirectly Accessed Registers} \\
\hline
\z{0x250} & HRW & \z{vsiselect}
                   & Virtual supervisor indirect register select \\
\z{0x251} & HRW & \z{vsireg}
                   & Virtual supervisor indirect register alias \\
\hline
\multicolumn{4}{|c|}{VS-Level Interrupts} \\
\hline
\z{0xEB0} & HRO & \z{vstopi}     & Virtual supervisor top interrupt \\
\hline
\multicolumn{4}{|c|}{VS-Level IMSIC Interface (only with an IMSIC)} \\
\hline
\z{0x258} & HRW & \z{vsseteipnum}
                   & VS set external interrupt-pending bit by number \\
\z{0x259} & HRW & \z{vsclreipnum}
                   & VS clear external interrupt-pending bit by number \\
\z{0x25A} & HRW & \z{vsseteienum}
                   & VS set external interrupt-enable bit by number \\
\z{0x25B} & HRW & \z{vsclreienum}
                   & VS clear external interrupt-enable bit by number \\
\z{0x25C} & SRW & \z{vstopei}    & Virtual supervisor top external interrupt \\
\hline
\multicolumn{4}{|c|}{Hypervisor and VS-Level High-Half CSRs (RV32 only)} \\
\hline
\z{0x613} & HRW & \z{hidelegh}   & Extension of \z{hideleg} \\
\z{0x618} & HRW & \z{hvienh}     & Extension of \z{hvien} \\
\z{0x655} & HRW & \z{hviph}      & Extension of \z{hvip} \\
\z{0x656} & HRW & \z{hviprio1h}  & Extension of \z{hviprio1} \\
\z{0x657} & HRW & \z{hviprio2h}  & Extension of \z{hviprio2} \\
\z{0x214} & HRW & \z{vsieh}      & Extension of \z{vsie} \\
\z{0x254} & HRW & \z{vsiph}      & Extension of \z{vsip} \\
\hline
\end{tabular}
\end{center}
\caption{Hypervisor and VS CSRs added by the Advanced Interrupt Architecture.}
\label{tab:CSRs-hypervisor}
\end{table*}

@@

Along the same lines, when \z{hstatus}.VGEIN is not the number of
an implemented guest external interrupt, attempts from \mbox{M-mode}
or \mbox{HS-mode} to access CSRs \z{vsseteipnum}, \z{vsclreipnum},
\z{vsseteienum}, or \z{vsclreienum} raise an illegal instruction
exception, and attempts from \mbox{VS-mode} to access \z{sseteipnum},
\z{sclreipnum}, \z{sseteienum}, \z{sclreienum}, or \z{stopei} raise a
virtual instruction exception.

>>>>

\begin{table*}[h!]
\begin{center}
\begin{tabular}{|l|l|l|l|}
\hline
Number & Privilege & Name        & Description \\
\hline
\hline
\multicolumn{4}{|c|}{%
  Virtual Interrupts and Interrupt Priorities for VS Level} \\
\hline
\z{0x608} & HRW & \z{hvien}      & Hypervisor virtual interrupt enables \\
\z{0x609} & HRW & \z{hvictl}     & Hypervisor virtual interrupt control \\
\z{0x646} & HRW & \z{hviprio1}   & Hypervisor VS-level interrupt priorities \\
\z{0x647} & HRW & \z{hviprio2}   & Hypervisor VS-level interrupt priorities \\
\hline
\multicolumn{4}{|c|}{VS-Level Window to Indirectly Accessed Registers} \\
\hline
\z{0x250} & HRW & \z{vsiselect}
                   & Virtual supervisor indirect register select \\
\z{0x251} & HRW & \z{vsireg}
                   & Virtual supervisor indirect register alias \\
\hline
\multicolumn{4}{|c|}{VS-Level Interrupts} \\
\hline
\z{0xEB0} & HRO & \z{vstopi}     & Virtual supervisor top interrupt \\
\hline
\multicolumn{4}{|c|}{VS-Level IMSIC Interface (only with an IMSIC)} \\
\hline
\z{0x258} & HRW & \z{vsseteipnum}
                   & VS set external interrupt-pending bit by number \\
\z{0x259} & HRW & \z{vsclreipnum}
                   & VS clear external interrupt-pending bit by number \\
\z{0x25A} & HRW & \z{vsseteienum}
                   & VS set external interrupt-enable bit by number \\
\z{0x25B} & HRW & \z{vsclreienum}
                   & VS clear external interrupt-enable bit by number \\
\z{0x25C} & HRW & \z{vstopei}    & Virtual supervisor top external interrupt \\
\hline
\multicolumn{4}{|c|}{Hypervisor and VS-Level High-Half CSRs (RV32 only)} \\
\hline
\z{0x613} & HRW & \z{hidelegh}   & Extension of \z{hideleg} \\
\z{0x618} & HRW & \z{hvienh}     & Extension of \z{hvien} \\
\z{0x655} & HRW & \z{hviph}      & Extension of \z{hvip} \\
\z{0x656} & HRW & \z{hviprio1h}  & Extension of \z{hviprio1} \\
\z{0x657} & HRW & \z{hviprio2h}  & Extension of \z{hviprio2} \\
\z{0x214} & HRW & \z{vsieh}      & Extension of \z{vsie} \\
\z{0x254} & HRW & \z{vsiph}      & Extension of \z{vsip} \\
\hline
\end{tabular}
\end{center}
\caption{Hypervisor and VS CSRs added by the Advanced Interrupt Architecture.}
\label{tab:CSRs-hypervisor}
\end{table*}

@@

Along the same lines, when \z{hstatus}.VGEIN is not the number of
an implemented guest external interrupt, attempts from \mbox{M-mode}
or \mbox{HS-mode} to access CSRs \z{vsseteipnum}, \z{vsclreipnum},
\z{vsseteienum}, \z{vsclreienum}, or \z{vstopei} raise an illegal instruction
exception, and attempts from \mbox{VS-mode} to access \z{sseteipnum},
\z{sclreipnum}, \z{sseteienum}, \z{sclreienum}, or \z{stopei} raise a
virtual instruction exception.
